Flexibility of interactions depends on habitat suitability

### 2019-08-30 paper/manuscript.Rmd
Add caption for random effects figure

```{r fig-random-effects, fig.width = width('single'), fig.height = 2.2*2.5, fig.cap = "Random effects"}
readd(fig_random_effects)
```

>>>>

```{r fig-random-effects, fig.width = width('single'), fig.height = 2.2*2.5, fig.cap = fig_random_effects_legend}
loadd(random_species_draws)

n_random_species <- random_species_draws %>%
  dplyr::group_by(guild) %>%
  dplyr::summarise(n_sp = dplyr::n_distinct(org_id))

n_random_pla <- n_random_species %>%
  dplyr::filter(guild == "pla_id")

n_random_ani <- n_random_species %>%
  dplyr::filter(guild == "ani_id")

fig_random_effects_legend <- 
  paste0("Species level effects of suitability. (a) Conditional effect of suitability for individual species. To facilitate visualization we show only species for which there is suitability information in at least six communities (", 
         n_random_pla, " plants and ", 
         n_random_ani, " pollinators). As in the previous figure, fitted values assume a hypothetical community of median size. In each panel we highlight two species for which the relationship between environental suitability and normalised degree was particularly strong. ", 
         "(b) The correlation between the species' intercept and the species' slope of suitability was negatively correlated.")

readd(fig_random_effects)
```
